\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-13 papers/jss/article.Rnw
Remove descriptor lookup section and incorporate a few sentences and the citation from that section into an earlier section where we first talk about the descriptorpool environment, per Jeroen's comment.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@771 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

After importing proto files, the corresponding message descriptors are
available from the \texttt{RProtoBuf:DescriptorPool} environment in 
the R search path. The underlying mechanism used here is
described in more detail in Section~\ref{sec-lookup}.

%JO: can we just move the section 7 to here? It's only one paragraph%

@@

@@

\section{Descriptor lookup}
\label{sec-lookup}

%JO: is this section really relevant? Maybe just a citation will do instead?

The \texttt{RProtoBuf} package uses the user defined tables framework
that is defined as part of the \texttt{RObjectTables} package available
from the OmegaHat project \citep{RObjectTables}.

The feature allows \texttt{RProtoBuf} to install the
special environment \emph{RProtoBuf:DescriptorPool} in the R search path.
The environment is special in that, instead of being associated with a
static hash table, it is dynamically queried by R as part of R's usual
variable lookup. In other words, it means that when the R interpreter
looks for a binding to a symbol (foo) in its search path,
it asks to our package if it knows the binding "foo", this is then
implemented by the \texttt{RProtoBuf} package by calling an internal
method of the \texttt{protobuf} C++ library.

>>>>

After importing proto files, the corresponding message descriptors are
available from the \texttt{RProtoBuf:DescriptorPool} environment in 
the R search path.  This environment is implemented with the user
defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.

%JO: can we just move the section 7 to here? It's only one paragraph%
%MS: I replaced section 7 with 2 sentences above.

@@

% The old section 7 in entirety:
%The \texttt{RProtoBuf} package uses the user defined tables framework
%that is defined as part of the \texttt{RObjectTables} package available
%from the OmegaHat project \citep{RObjectTables}.
%
%The feature allows \texttt{RProtoBuf} to install the
%special environment \emph{RProtoBuf:DescriptorPool} in the R search path.
%The environment is special in that, instead of being associated with a
%static hash table, it is dynamically queried by R as part of R's usual
%variable lookup. In other words, it means that when the R interpreter
%looks for a binding to a symbol (foo) in its search path,
%it asks to our package if it knows the binding "foo", this is then
%implemented by the \texttt{RProtoBuf} package by calling an internal
%method of the \texttt{protobuf} C++ library.

@@
